validateHOT - Validate your Holdout Task

### 2023-10-22 README.Rmd
paper updated - 231023

@@

Orme, B. K. (2020). <em>Getting Started with Conjoint Analysis: Strategies for Product Design and Pricing Research</em>. 4th edition. Manhattan Beach, CA: Research Publishers LLC.

>>>>

### Reestimating raw utilities

<code>validateHOT</code> also provides 2 functions to better interpret the scores of both (A)CBC and MaxDiff. Currently, two functions are provided, namely:

<ul>
<li><code>att_imp()</code>: converts the raw utilities of either an ACBC or CBC into importance scores for each attribute (see, Orme, 2020, pp. 79-81)</li>

<li><code>prob_scores()</code>converts the raw utilities of a MaxDiff to choice probabilities by applying the following procedures:
<ul><li>For unanchored MaxDiff: First, the scores are zero-centered, afterwards they are transformed by the following formula $\frac{exp^{U_i}}{(exp^{U_i} + a - 1)}$ (Chrzan & Orme, 2019, p. 56), where *$U_i$* is the raw utility of item *i* and <code>a</code> is the number of items shown simultaneously per MaxDiff task. Finally, the scores are normalized.</li>
<li>For anchored MaxDiff: $\frac{exp^{U_i}}{(exp^{U_i} + a - 1)} * 100 * \frac{1}{a}$ (Chrzan & Orme, 2019, p. 59).</li>
</ul>
</li>
</ul>

@@

Orme, B. K. 2020. <em>Getting Started with Conjoint Analysis: Strategies for Product Design and Pricing Research</em>. 4th edition. Manhattan Beach, CA: Research Publishers LLC.

### 2023-10-22 paper/paper.Rmd
paper updated - 231023

---
title: 'validateHOT - Validate your Holdout Task'
tags:
  - R
authors:
  - name: Joshua Schramm
    orcid: 0000-0001-5602-4632
    corresponding: True
    affiliation: 1
affiliations:
 - name: Chemnitz University of Technology, Germany
   index: 1
citation_author: Schramm, J.
date: 10 October 2023
year: 2023
bibliography: paper.bib
link-citations: true
output: rticles::joss_article
journal: JOSS
---

@@

# Summary
validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained a (adaptive) choice-based conjoint analysis and MaxDiff using [Sawtooth Software](https://sawtoothsoftware.com/). Having valid data is essential to predict future choice behavior.

dfsdfdjf

@@

```{r}
data("MaxDiff")
HOT <- createHOT(
  data = MaxDiff, # data frame
  id = 1, # column index of unique identifier
  None = 19, # column index of none alternative
  prod = 7, # no of alternatives in HOT excluding none
  prod.levels = list(3, 10, 11, 15, 16, 17, 18), # column index of alternatives
  method = "MaxDiff", # method applied
  choice = 20 # column index of choice alternative
)
```

@@

# Availability
validateHOT is available on [Github](https://github.com/JoshSchramm94/validateHOT).

>>>>

---
title: 'validateHOT - Validate your Holdout Task'
tags:
  - R
  - MaxDiff
  - Conjoint Analysis
  - Market Simulations
  - Predictive Validity
authors:
  - name: Joshua Schramm
    orcid: 0000-0001-5602-4632
    corresponding: True
    affiliation: 1
  - name: Marcel Lichters
    orcid: 0000-0002-3710-2292
    corresponding: FALSE
    affiliation: 1, 2    
affiliations:
 - name: Chemnitz University of Technology, Germany
   index: 1
 - name: Otto von Guericke University of Magdeburg, Germany
   index: 1
citation_author: Schramm & Lichters.
date: 22 October 2023
year: 2023
bibliography: paper.bib
link-citations: true
output: rticles::joss_article
journal: JOSS
---

@@

# Summary

validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using [Sawtooth Software](https://sawtoothsoftware.com/). The ultimate goal of preference measurement techniques such as (A)CBC or MaxDiff is to predict future behavior [@green1990]. Therefore, it is essential for both academics and practitioners to ensure that the collected data is valid and can also predict outside tasks. The easiest way to test this is to include so-called holdout or validation task [@Orme2015]. Despite the important role of validation tasks, most of the conjoint studies done in practice do not include them [@yang2018], which is unsatisfactory, given the fact that the model is used to estimate market shares which is the basis for relevant marketing decisions.

validateHOT combines both validation and market simulation in one package. validateHOT's advantages are the following: a) it helps you to decide which is the best model to proceed by validating it, b) it runs relevant market simulations that help to find the right product combinations, and finally, c) it is open source tool for function that are usually implemented in Sawtooth Software and are ofen a black-box for researchers and practitioners.

@@

```{r}
data("MaxDiff")
HOT <- createHOT(
  data = MaxDiff, # data frame
  id = 1, # index unique identifier
  none = 19, # index of none alternative
  prod = 7, # no of alternatives in HOT excluding none
  prod.levels = list(3, 10, 11, 15, 16, 17, 18), # index of alternatives
  method = "MaxDiff", # method applied
  choice = 20 # column index of choice alternative
)
```

@@

# Availability

validateHOT is available on [Github](https://github.com/JoshSchramm94/validateHOT).
